### 2019-05-31 main-plos-singlefile.tex
supp.

The AUC values for the top-1\% texture features based on T₂w, ADCₘ, ADCₖ, K,
and T₂ are shown in supporting material Tables S2, S4, S6, S8, and S10,
respectively. Similarly, AUCs for the statistical features for each image
type are shown in supporting material Tables S3, S5, S7, S9, and S11.

@@

Supporting Material is available at \url{http://mrc.utu.fi/data}. Program code
is available at \url{https://github.com/jupito/dwilib}.

@@

\paragraph*{S1 File.}
\label{S1_File}
{\bf Supporting Tables.}
Patient characteristics; best features of each image type; features in final
proposed model; best features' correlation coefficients among image types.

\paragraph*{S2 File.}
\label{S2_File}
{\bf Supporting Figures.}
Files DWI-Mono-ADCm-xxx.png, T2-fitted-xxx.png, and T2w-std-xxx.png correspond
to ADCm and T2 parametric maps, and T2-weighted images of each patient,
respectively. On the first row of slices they show positions of regions of
interest placed on the prostate cancer lesions (red, yellow) and around whole
prostate (white). The prostate mask is on the second row, while the remaining
rows are lesion masks. Files histology-xx.jpg contain the whole mount
prostatectomy sections of each patient, with tumor outlines in green. Please
note that identical MRI acquisition protocol has been used on all patients,
including slice thickness. Here all prostate cancer masks are show with
corresponding whole mount prostatectomy sections.

\paragraph*{S3 File.}
\label{S3_File}
{\bf Lesion Radiomics.}
This file contains 7105 radiomics calculated for each 100 lesion from 62
patients in CSV format (comma-separated values). The first column contains the
patient ID number. The second column contains the Gleason score group used for
classifying: --1 for low score group, 1 for high score group. The rest of the
columns are the calculated feature averages over each lesion. The first row with
column description contains the feature names.

>>>>

The AUC values for the top-1\% texture features based on T₂w, ADCₘ, ADCₖ, K,
and T₂ are shown in Supporting Material Tables S2, S4, S6, S8, and S10,
respectively. Similarly, AUCs for the statistical features for each image
type are shown in Supporting Material Tables S3, S5, S7, S9, and S11.

@@

Supporting Material is available at \url{http://mrc.utu.fi/data}. Program code
used for calculations is available at \url{https://github.com/jupito/dwilib}.

@@

\paragraph*{File S1.}
\label{S1_File}
{\bf Supporting Tables.}
Patient characteristics; best features of each image type; features in final
proposed model; best features' correlation coefficients among image types.

\paragraph*{File S2.}
\label{S2_File}
{\bf Supporting Figures.}
Files DWI-Mono-ADCm-xxx.png, T2-fitted-xxx.png, and T2w-std-xxx.png correspond
to ADCm and T2 parametric maps, and T2-weighted images of each patient,
respectively. On the first row of slices they show positions of regions of
interest placed on the prostate cancer lesions (red, yellow) and around whole
prostate (white). The prostate mask is on the second row, while the remaining
rows are lesion masks. Files histology-xx.jpg contain the whole mount
prostatectomy sections of each patient, with tumor outlines in green. Please
note that identical MRI acquisition protocol has been used on all patients,
including slice thickness. Here all prostate cancer masks are show with
corresponding whole mount prostatectomy sections.

\paragraph*{File S3.}
\label{S3_File}
{\bf Lesion Radiomics.}
This file contains 7105 radiomics calculated for each 100 lesion from 62
patients in CSV format (comma-separated values). The first column contains the
patient ID number. The second column contains the Gleason score group used for
classifying: --1 for low score group, 1 for high score group. The rest of the
columns are the calculated feature averages over each lesion. The first row with
column description contains the feature names.
